Predicting the transmission of COVID-19 using inter and intra-county mobility: a mathematical modelling study

### 2022-12-22 Manuscripts/main.tex
Update model

\begin{center}
    \begin{table}[h]
    \caption{Convolutional kernels in the model as probability distributions}
    \centering
\begin{tabular}[H]{p{2cm}p{6cm}p{4cm}p{4cm}}
     \textbf{Parameter}& \textbf{Description}  & \textbf{Value}& \textbf{Reference} \\
     \midrule
     $d_E$ & Latent period ($E$ to $I_p$ and $E$ to $I_s$) & $\sim gamma(2.5,4)$ & Davies et al.\\
     $d_c$ & Duration of clinical infectiousness& $\sim gamma(2.5,4)$ &  \\
     $d_s$ & Duration of sub-clinical infectiousness& $\sim gamma(5,4)$ &  \\
     $d_{pos}$ & Duration of PCR positivity& $\sim normal(9.87, 0.25)$ & \\ 
     $d_{hosp}$ & Duration from PCR positivity to hospitalization& $\sim normal(7.5, 1)$ & \\ 
     $d_{ICU}$ & Duration from hospitalization to ICU& $\sim normal(3.6, 1)$ & \\ 
     $d_{R,hosp}$ & Average stay in hospital& $\sim normal(11.08, 1.2)$ & \\ 
     $d_{R,ICU}$ & Average stay in ICU & $\sim normal(3.6, 1)$ & \\ 
\end{tabular}
\end{table}
\end{center}

\begin{align*}
    P(Hosp|Clinical) = /
\end{align*}
We defined following variables with their corresponding meaning. Each variable is a real-valued function $\cdot: \text{date} \to \R^+$.
\begin{align*}
    S & := \ \text{Number of susceptible individuals}\\
    E & := \ \text{Number of exposed individuals}\\
    I & := \ \text{Number of infected individuals}\\
    I_s &:= \text{Number of subclinical infected individuals}\\
    I_p &:= \text{Number of preclinical infected individuals}\\
    I_c &:= \text{Number of clinical infected individuals}\\
    I_h &:= \text{Number of hospitalized infected individuals}\\
    I_{ICU} &:= \text{Number of ICU-hospitalized infected individuals}\\
    R & := \ \text{Number of removed individuals}\\
    r & := \ \text{Number of recovered individuals}\\
    D & := \ \text{Number of deceased individuals}\\ 
\end{align*}
We define the following notations to represent the change of variables:
\begin{align*}
    \Delta \ \cdot &:= \ \text{Number of individuals transformed into a specific state within a time step}\\
    \delta \ \cdot &:= \ \text{Number of individuals transformed out from a specific state within a time step}\\
    d \ \cdot &:= \ \text{chahnge of the number of individuals transformed out from a specific state within a time step}\\
\end{align*}
We define the following transition functions:
\subsection*{Susceptible to exposed}
\begin{align*}
    \Delta S(t) &= \overbrace{\vect{\Delta R(t) - \Delta D(t)}}^{= \Delta r(t)}\\
    \delta S(t) &= - \Delta E(t)\\
    dS(t) &=  \Delta S(t) - \delta S(t) = \overbrace{\vect{\Delta R(t) - \Delta D(t)}}^{= \Delta r(t)} - \Delta E
\end{align*}

\subsection*{Exposed to infected}
\subsubsection*{Exposed to subclinically-infected}
\begin{align*}
    \Delta I_s(t) &= \vect{E * f_{d_s}  }(t) \circ  sub\_ratio \\
    \delta I_s(t) &= \vect{I_s * f_{d_{s}}} (t) \\
    d I_s(t) &=  \Delta I_s(t)  -  \delta I_s (t)
\end{align*}

\subsubsection*{Exposed to pre-clinically infected}
\begin{align*}
    \Delta I_p(t) &= \vect{E * f_{d_p} }(t) \circ  cli\_ratio \\
    \delta I_p(t) &= \vect{I_p(t) * f_{d_{c}}} (t) \\
    d I_p(t) &=  \Delta I_p (t)  -  \delta I_p (t)
\end{align*}

\subsection*{Exposed to all-type of infected indeviduals}
\begin{align*}
    \Delta I &= \Delta I_s + \Delta I_p\\
    \delta I &= \delta I_s + \delta I_p\\
    d I &= d I_s + d I_p\\
\end{align*}

\subsection*{Transition within infected}
\subsubsection*{Pre-clinical infected to clinical infected}
\begin{align*}
    \Delta I_c &= \vect{I_p * f_{d_c}} (t)\\
    \delta I_c &= \vect{I_c * f_{d_r - d_c}} (t)\\
\end{align*}

>>>>

\begin{center}
    \begin{table}[h]
    \caption{Convolutional kernels in the model as probability distributions}
    \centering
\begin{tabular}[H]{p{2cm}p{6cm}p{4cm}p{3cm}}
     \textbf{Parameter}& \textbf{Description}  & \textbf{Value}& \textbf{Reference} \\
     \midrule
     $d_E$ & Latent period ($E$ to $I_p$ and $E$ to $I_s$) & $\sim gamma(2.5,4)$ & Davies et al.\\
     $d_c$ & Duration of clinical infectiousness& $\sim gamma(2.5,4)$ &  Davies et al.\\
     $d_s$ & Duration of sub-clinical infectiousness& $\sim gamma(5,4)$ &  Davies et al.\\
     $d_{pos}$ & Duration of PCR positivity& $\sim normal(9.87, 0.25)$ & [REF]\\ 
     $d_{hosp}$ & Duration from PCR positivity to hospitalization& $\sim normal(7.5, 1)$ & Davies et al.\\ 
     $d_{ICU}$ & Duration from hospitalization to ICU& $\sim normal(3.6, 1)$ & Davies et al.\\ 
     $d_{R,hosp}$ & Average stay in hospital & $\sim normal(11.08, 1.2)$ & Davies et al.\\ 
     $d_{R,ICU}$ & Average stay in hospital & $\sim normal(13.33, 1.2)$ & Davies et al.
    \end{tabular}
\end{table}
\end{center}

\begin{center}
    \begin{table}[h]
    \caption{Age-specific odds}
    \centering
\begin{tabular}[H]{p{3cm}p{5cm}p{4cm}p{3cm}}
     \textbf{Parameter}& \textbf{Description}  & \textbf{Value}& \textbf{Reference} \\
     \midrule
     $susc\_ratio$ & Relative susceptibility to infection by age & 0.39 - 0.86 & Davies et al.\\
     $clin\_ratio$ & Clinical fraction by age &  0.23 - 0.71  &  Davies et al.\\
     $hosp\_ratio$ & Hospitalization ratio of clinical cases by age & 0.009 - 0.21 &  [REF]\\
     $icu\_ratio$ & ICU hospitalized ratio of clinical cases by age & 0.001 - 0.028 &  [REF]\\
     $cfr\_ratio$ & Case-fatality ratio by age& 0.00009 - 0.09 &  [REF]\\
     $work\_ratio$ & Working force ratio by age& DoG interpolation &  [REF]\\
     $sch\_ratio$ & School ratio by age & DoG interpolation &  [REF]
    \end{tabular}
\end{table}
\end{center}

\newpage

\begin{align*}
    P(Hosp|Clinical) = /
\end{align*}
We defined following variables with their corresponding meaning. Each variable is a real-valued function $\cdot: \text{date} \to \R^+$.
\begin{align*}
    S & := \ \text{Number of susceptible individuals}\\
    E & := \ \text{Number of exposed individuals}\\
    I & := \ \text{Number of infected individuals}\\
    I_s &:= \text{Number of subclinical infected individuals}\\
    I_p &:= \text{Number of preclinical infected individuals}\\
    I_c &:= \text{Number of clinical infected individuals}\\
    I_h &:= \text{Number of hospitalized infected individuals}\\
    I_{ICU} &:= \text{Number of ICU-hospitalized infected individuals}\\
    R & := \ \text{Number of removed individuals}\\
    r & := \ \text{Number of recovered individuals}\\
    D & := \ \text{Number of deceased individuals}\\ 
\end{align*}
We define the following notations to represent the change of variables:
\begin{align*}
    \Delta \ \cdot &:= \ \text{Number of individuals transformed into a specific state within a time step}\\
    \delta \ \cdot &:= \ \text{Number of individuals transformed out from a specific state within a time step}\\
    d \ \cdot &:= \ \text{chahnge of the number of individuals transformed out from a specific state within a time step}\\
\end{align*}
We define the following transition functions:
\subsection*{Susceptible to exposed}
\begin{align*}
    \Delta E (t) &= susc_ratio \circ M^x I(x)
\end{align*}
\begin{align*}
    \Delta S(t) &= \overbrace{\vect{\Delta R(t) - \Delta D(t)}}^{= \Delta r(t)}\\
    \delta S(t) &= - \Delta E(t)\\
    dS(t) &=  \Delta S(t) - \delta S(t) = \overbrace{\vect{\Delta R(t) - \Delta D(t)}}^{= \Delta r(t)} - \Delta E
\end{align*}

\subsection*{Exposed to infected}
\subsubsection*{Exposed to subclinical infection}
\begin{align*}
    \Delta I_s(t) &= \vect{E * f_{d_s}  }(t) \circ \vect{1_{16} - clin\_ratio} \\
    \delta I_s(t) &= \vect{I_s * f_{d_{s}}} (t)
\end{align*}

\subsubsection*{Exposed to pre-clinical infection}
\begin{align*}
    \Delta I_p(t) &= \vect{E * f_{d_p} }(t) \circ  clin\_ratio \\
    \delta I_p(t) &= \vect{I_p(t) * f_{d_{c}}} (t)
\end{align*}

\subsection*{Exposed to all-type of infected indeviduals}
\begin{align*}
    \Delta I &= \Delta I_s + \Delta I_p\\
    \delta I &= \delta I_s + \delta I_p\\
    d S(t) &= \vect{\Delta I_s + \Delta I_p } - \vect{\delta I_s + \delta I_p}
\end{align*}

\subsection*{Transition within infected}
\subsubsection*{Pre-clinical infection to clinical infection}
\begin{align*}
    \Delta I_c &= \vect{I_p * f_{d_c}} (t)\\
    \delta I_c &= \vect{I_c * f_{d_{pos}}} (t)
\end{align*}
